Supplemental material for `Eliminating prior-bias from sparse-projection tomographic reconstructions'

### 2020-07-20 paper/supplementary.tex
edited figures,supplemetary material

%-----------------------------Sprouts (154 angles)--------------------------
\newpage
\subsection{Reconstruction from 154 projection views}
\begin{figure}[h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/colorTestIm.png}
        \caption{Test image}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/fbp.png}
        \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/cs_dct.png}
        \caption{CS-DCT}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/cs_wavelet.png}
        \caption{CS-wavelet}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/plain_pca.png}
        \caption{prior unselective+cs}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/weighted_pca5.png}
        \caption{our method}
     \end{subfigure}
     \caption{Reconstruction of sprouts [260 x 260] image from measurements obtained by $83\%$ sampling (154 projection views).} 
\label{fig:joint}
\end{figure}
----------------------------------------------------------------------------------------------------------------------------------
\bibliography{tci_ref}
\end{document}

>>>>

%-----------------------------Sprouts (154 angles)--------------------------
\newpage
\subsection{Reconstruction from 154 projection views}
\begin{figure}[h]
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/colorTestIm.png}
        \caption{Test image}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/fbp.png}
        \caption{FBP}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/cs_dct.png}
        \caption{CS-DCT}
     \end{subfigure}
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/cs_wavelet.png}
        \caption{CS-wavelet}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/plain_pca.png}
        \caption{prior unselective+cs}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.3\linewidth}
        \includegraphics[width=\textwidth]{../images/supplementary/2D_sprouts/154_angles/1/weighted_pca5.png}
        \caption{our method}
     \end{subfigure}
     \caption{Reconstruction of sprouts [260 x 260] image from measurements obtained by $83\%$ sampling (154 projection views).} 
\label{fig:joint}
\end{figure}
\newpage
%--------------------------BIG images: TMH results
\section{Bigger images for reconstruction results shown in main paper}
\subsection{Liver}
%-------RFA2 moderate views
\textbf{Goal: Observe details of new changes}
\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{white}{blue}{\includegraphics[width=0.49\columnwidth]{../images/tmh/RFA2/few_views/colorTestIm.png}}}\hfill
\subcaptionbox{FBP}{\includegraphics[width=0.49\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}}\hfill
\subcaptionbox{l1-ls}{\includegraphics[width=0.49\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}}\hfill
\subcaptionbox{Spatially-varying prior}{\includegraphics[width=0.49\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}}
\caption[Representative results-2]{Reconstruction of Liver corresponding to Figure 8 of the main paper.}
\label{fig:RFA2_few_views_biggerIm}
\end{figure}
\newpage

\textbf{Test image Figure~\ref{fig:RFA2_few_views_biggerIm}  is shown in larger display here  again for better clarity.}\\
\begin{figure}[!h]
\centering
\includegraphics[width=1.2\columnwidth]{../images/tmh/RFA2/few_views/colorTestIm.png}
\captionsetup{labelformat=empty}
\caption[Representative results-2]{\large{Test slice}}
\label{fig:RFA2_few_views_bigger}
\end{figure}
\newpage
\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm}  is shown in larger display here  again for better clarity.}\\
\begin{figure}[!h]
\centering
\includegraphics[width=1.2\columnwidth]{../images/tmh/RFA2/few_views/fbp.png}
\captionsetup{labelformat=empty}
\caption[Representative results-2]{\large{FBP}}
\label{fig:RFA2_few_views_bigger}
\end{figure}
\newpage
\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm}  is shown in larger display here  again for better clarity.}\\
\begin{figure}[!h]
\centering
\includegraphics[width=1.2\columnwidth]{../images/tmh/RFA2/few_views/cs_dct.png}
\captionsetup{labelformat=empty}
\caption[Representative results-2]{\large{l1-ls}}
\label{fig:RFA2_few_views_bigger}
\end{figure}
\newpage
\textbf{Reconstruction result of Figure~\ref{fig:RFA2_few_views_biggerIm} is shown in larger display here  again for better clarity.}\\
\begin{figure}[!h]
\centering
\includegraphics[width=1.2\columnwidth]{../images/tmh/RFA2/few_views/weighted_pca_all_methods_kk_0_01.png}
\captionsetup{labelformat=empty}
\caption[Representative results-2]{\large{Spatially-varying prior method}}
\label{fig:RFA2_few_views_bigger}
\end{figure}
\newpage

%------------------------------------Bigger images for Sprouts------------------
\textbf{Sprouts:}

\begin{figure}[!h]
    \begin{subfigure}[b]{0.4\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
%\captionsetup{labelformat=empty}
        \caption{Test}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}
%\captionsetup{labelformat=empty}
        \caption{FDK}
    \end{subfigure}
\quad
    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/csIm.png}
%\captionsetup{labelformat=empty}
        \caption{l1-ls}
     \end{subfigure}\\
\quad
    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}
%\captionsetup{labelformat=empty}
        \caption{Uniform\\ Prior}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\textwidth]{../images/sprouts/weightedPriorIm.png}
%\captionsetup{labelformat=empty}
        \caption{Spatially-Varying\\ prior}
    \end{subfigure}
    %\quad
    %\captionsetup{labelformat=empty}
     \caption{Reconstruction of sprouts corresponding to Figure 16 of the main paper.} 
\label{fig:sprouts_3D_results_biggerIm}
%\addtolength{\textfloatsep}{-0.8cm}
\end{figure}

\newpage
\textbf{Test image of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}\\
\begin{figure}[!h]
    \begin{subfigure}[b]{\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/testIm_red.png}}
\captionsetup{labelformat=empty}
        \caption{\large{Test}}
     \end{subfigure}
\end{figure}
\newpage
\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}\\
\begin{figure}[!h]
    \begin{subfigure}[b]{\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/fdkIm.png}}
\captionsetup{labelformat=empty}
        \caption{\large{FDK}}
     \end{subfigure}
\end{figure}
\newpage
\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}\\
\begin{figure}[!h]
    \begin{subfigure}[b]{\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/csIm.png}}
\captionsetup{labelformat=empty}
        \caption{\large{l1-ls}}
     \end{subfigure}
\end{figure}
\newpage
\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}\\
\begin{figure}[!h]
    \begin{subfigure}[b]{\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/plainPriorIm.png}}
\captionsetup{labelformat=empty}
        \caption{\large{Uniform Prior}}
     \end{subfigure}
\end{figure}
\newpage
\textbf{Reconstruction result of Figure~\ref{fig:sprouts_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}\\
\begin{figure}[!h]
    \begin{subfigure}[b]{\linewidth}
        \fcolorbox{green}{green}{\includegraphics[width=\textwidth]{../images/sprouts/weightedPriorIm.png}}
\captionsetup{labelformat=empty}
        \caption{\large{Spatially-Varying Prior}}
     \end{subfigure}
\end{figure}
\newpage

%--------------------------------Bigger results for Okra------------------------
\textbf{Okra:}

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\fcolorbox{yellow}{yellow}{\includegraphics[width=0.2\columnwidth]{../images/okra/testCropped.png}}}\hfill
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.2\columnwidth]{../images/okra/fdk_cropped.png}}\hfill
\subcaptionbox{l1-ls}{\includegraphics[width=0.2\columnwidth]{../images/okra/cs_cropped.png}}\hfill
\subcaptionbox{\mbox{Uniform}\\prior}{\includegraphics[width=0.2\columnwidth]{../images/okra/pca_cropped.png}}\hfill
\subcaptionbox{Spatially-Varying\\ prior}{\includegraphics[width=0.2\columnwidth]{../images/okra/prior_weighted_cropped.png}}
\caption{Reconstruction of okra corresponding to Figure 14 of the main paper.}
\label{fig:okra_3D_results_biggerIm}
\end{figure}
\newpage
\textbf{Test image of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
\begin{figure}[!h]
\centering
       \includegraphics[width=0.5\columnwidth]{../images/okra/testCropped.png}
\captionsetup{labelformat=empty}
        \caption{\large{Test}}
\end{figure}
\newpage

\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
\begin{figure}[!h]
\centering
       \includegraphics[width=0.5\columnwidth]{../images/okra/fdk_cropped.png}
\captionsetup{labelformat=empty}
        \caption{\large{FDK}}
\end{figure}
\newpage

\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
\begin{figure}[!h]
\centering
       \includegraphics[width=0.5\columnwidth]{../images/okra/cs_cropped.png}
\captionsetup{labelformat=empty}
        \caption{\large{l1-ls}}
\end{figure}
\newpage

\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
\begin{figure}[!h]
\centering
       \includegraphics[width=0.5\columnwidth]{../images/okra/pca_cropped.png}
\captionsetup{labelformat=empty}
        \caption{\large{Uniform Prior}}
\end{figure}
\newpage

\textbf{Reconstruction result of Figure~\ref{fig:okra_3D_results_biggerIm}  is shown in larger display here  again for better clarity.}
\begin{figure}[!h]
\centering
       \includegraphics[width=0.5\columnwidth]{../images/okra/prior_weighted_cropped.png}
\captionsetup{labelformat=empty}
        \caption{\large{Spatially-Varying prior}}
\end{figure}
\newpage

%----------------------------------Comparison with Literature------------------------
\section{Detecting new changes directly in the measurements}
Sec.2 of the main paper (`Related work') contrasts the spatially-varying technique  with other prior based techniques in literature. Here we present a 2D reconstruction  result (of the test shown in Figure.~\ref{fig:comparisonLit_dataset}) to compare our method with~\cite{Lee2012}, in which the new changes are directly detected in the measurement space by computing the difference between the measurements of the test and the corresponding simulated measurements of the template. This difference-volume is then reconstructed and then fused (added to) with the original high quality template. However, in the above method, the sub-sampling artefacts present in the difference-volume gets carried over to the final reconstructed image. This is shown in Figure~\ref{fig:comparisonLit_results}. A quantitative comparison over the region of interest is shown in Table~\ref{tab:comparisonLit}.
\begin{figure}[!h]
    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/template_3.png}
%\captionsetup{labelformat=empty}
        \caption{Template}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\textwidth]{../images/potato/testIm_color.png}
%\captionsetup{labelformat=empty}
        \caption{Test}
    \end{subfigure}
    %\captionsetup{labelformat=empty}
     \caption{Template and test from the Potato dataset for the reconstructions shown in Figure.~\ref{fig:comparisonLit_results}} 
\label{fig:comparisonLit_dataset}
%\addtolength{\textfloatsep}{-0.8cm}
\end{figure}
\newpage

\begin{figure}[!h]
    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\textwidth]{../images/comparison_lit/result_new_changes.png}
%\captionsetup{labelformat=empty}
        \caption{~\cite{Lee2012}:new-changes}
     \end{subfigure}
\quad
    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\textwidth]{../images/comparison_lit/result_literature_test.png}
%\captionsetup{labelformat=empty}
        \caption{~\cite{Lee2012}:Reconstruction}
    \end{subfigure}

    \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\textwidth]{../images/comparison_lit/weightsIm_all_methods30.png}
%\captionsetup{labelformat=empty}
        \caption{Our weights-map}
    \end{subfigure}
   \quad
        \begin{subfigure}[b]{0.4\linewidth}
        \includegraphics[width=\textwidth]{../images/comparison_lit/weighted_pca_all_methods30.png}
%\captionsetup{labelformat=empty}
        \caption{Our Reconstruction}
    \end{subfigure}
    %\captionsetup{labelformat=empty}
     \caption{Reconstruction of the test in Figure~\ref{fig:comparisonLit_dataset}.  Reconstructions were performed from 12 views. Gaussian noise of 0 mean and SD = $1\%$ of mean of measurements, was added to the measurements.} 
\label{fig:comparisonLit_results}
%\addtolength{\textfloatsep}{-0.8cm}
\end{figure}

\begin{table}[!h]
  \centering
      \caption{SSIM values (within RoI) of reconstructions shown in Figure~\ref{fig:comparisonLit_results}}
  \begin{tabular}{|l|l|l|}
\hline
 & \textbf{SSIM (whole image)} & \textbf{SSIM (RoI)} \\ \hline
\textbf{Method in~\cite{Lee2012}} & 0.65 & 0.60 \\ \hline
\textbf{\begin{tabular}[c]{@{}l@{}}Spatially-varying \\prior\end{tabular}} & 0.89 & 0.92 \\ \hline
  \end{tabular}
  \label{tab:comparisonLit}
\end{table}

\bibliography{tci_ref}
\end{document}
